Business Consultant / Information Technology (IT) Specialist – Entry LIntroductionAt IBM, work is more than a job - it's a calling: To build. To design. To code. To consult. To think along with clients and sell. To make markets. To invent. To collaborate. Not just to do something better, but to attempt things you've never thought possible. Are you ready to lead in this new era of technology and solve some of the world's most challenging problems? If so, lets talk.Your Role and ResponsibilitiesAt IBM we know technology. But technology is only as good as the results it delivers. Are you interested and adept in application development methodology and tools? The IBM Services Centre: Nova Scotia occupies a unique position in the IT marketplace – at the intersection of business and technology. This Global Service Centre provides services to leading edge clients who are looking for a unique, Canada – based capability to design, develop and support their mission-critical applications.As a member of our team, you will help clients solve some of their most challenging business problems, capitalize on market opportunities and achieve real value in today’s tough economy.The Business Consultant / Information Technology (IT) Specialist roles are embedded into a variety of our business solutions and opportunities. Business Consultants are involved in business analysis, project management and support, as well as solution design for client engagements. IT Specialists are involved in the design and development of applications to meet client requirements, in addition to preparing executing various test cases. As part of our team, you will be able to leverage the advanced methodologies, tools and procedures that only a global leader like IBM can provide. You will also have the opportunity to develop new custom applications and solution designs to broaden your skills and grow your career in the IT and business communities.What will the role offer you?* The opportunity to work with top IBM clients from around the world* The chance to live and work in Nova Scotia, Canada* Exceptional training and on-going learning and development opportunities* Multiple career growth opportunities* A supportive work environment* Competitive salary and benefitsWe are hiring year round, so if you are looking for an impactful and rewarding career in an exciting fast paced work environment – apply today!What are we looking for in a successful candidate?* Capabilities / experiences in business consultancy, project management, strategic thinking, data security and privacy, business controls, financial analysis* Information Technology experience or demonstrated technical aptitude obtained either through relevant coursework or work-related activities* Relevant business experience or Industry experience in the Telecommunications, Retail, Financial Services Sector – Banking and Insurance, Energy, Public Sector – Healthcare and Federal* Capabilities in any of the following Technologies: SAP, Oracle/ PeopleSoft, Siebel, PJava, C++, C#, J2EE, HTML5, jQuery, CSS, .NET, XML, Web 2.0, Technology Spring, Hibernate, Javascript, Java Swing, Ruby on Rails, PHP, Filenet, Maximo, Worklight, Dojo, Mobile Application Development and/ or Business Intelligence/ Analytics Software.* A demonstrated history of achievement in academics, internships, and/or work experience* Ability to thrive in a team environment, making individual contributions to challenging projects* Ability to handle multiple tasks concurrently and to meet deadlines* Proven interpersonal, writing, and verbal communication skill* Demonstrated leadership abilities* Programming experience or background in any language* Willingness to live in Nova Scotia (a low amount of travel anticipated)Required Technical and Professional Expertise* N/APreferred Technical and Professional Expertise* N/AAbout Business UnitIBM Services is a team of business, strategy and technology consultants that design, build, and run foundational systems and services that is the backbone of the world's economy. IBM Services partners with the world's leading companies in over 170 countries to build smarter businesses by reimagining and reinventing through technology, with its outcome-focused methodologies, industry-leading portfolio and world class research and operations expertise leading to results-driven innovation and enduring excellence.Your Life @ IBMWhat matters to you when you’re looking for your next career challenge?Maybe you want to get involved in work that really changes the world? What about somewhere with incredible and diverse career and development opportunities – where you can truly discover your passion? Are you looking for a culture of openness, collaboration and trust – where everyone has a voice? What about all of these? If so, then IBM could be your next career challenge. Join us, not to do something better, but to attempt things you never thought possible.Impact. Inclusion. Infinite Experiences. Do your best work ever.About IBMIBM’s greatest invention is the IBMer. We believe that progress is made through progressive thinking, progressive leadership, progressive policy and progressive action. IBMers believe that the application of intelligence, reason and science can improve business, society and the human condition. Restlessly reinventing since 1911, we are the largest technology and consulting employer in the world, with more than 380,000 IBMers serving clients in 170 countries.Location StatementThis role will involve working with technology that is covered by Export Regulations sanctions. If you are a Foreign National from any of the following US sanctioned countries (Cuba, Iran, North Korea, Sudan, and Syria) on a work permit, you are not eligible for employment in this position.Being You @ IBMIBM is committed to creating a diverse environment and is proud to be an equal opportunity employer. All qualified applicants will receive consideration for employment without regard to race, color, religion, gender, gender identity or expression, sexual orientation, national origin, genetics, disability, age, or veteran status. IBM is also committed to compliance with all fair employment practices regarding citizenship and immigration status.